Proposed Solution

### 2017-01-20 CAV17/secs/abs.tex
reorganize and add main points

>>>>

\app is capable of detecting various errors that cannot
be detected by previous efforts,
including entry ordering errors, fine-grained value correlation errors, 
and missing entry errors.

System failures resulting from configuration errors 
are major reasons for compromised availability and
reliability of today's software systems.
Although many misconfiguration handling techniques
such as checking, troubleshooting, and repair
have been proposed, 
offering automatic verification for configuration files -- as often  
done for regular programs -- is still an open problem.
This is because software configurations are typically written in
poorly structured and untyped ``languages'', and 
specifying constraints and rules for configuration 
verification is non-trivial in practice.

This paper presents \app, the first automatic verification framework for
general software configurations.
\app verifies a target configuration file $F$ through three steps.
Firstly, \app analyzes a dataset containing many sample configuration 
files belonging to the same system as $F$,
translating these sample files to a
well-structured and probabilistically-typed 
intermediate representation.
Secondly, \app derives rules and constraints by analyzing
this intermediate representation, thus building a
sophisticated language model.
Finally, \app uses the resulting language model to verify $F$.
The \app framework is highly modular, 
does not rely on system source code, and
can be applied to any new configuration file type with minimal user input.

### 2017-01-20 CAV17/secs/intro.tex
reorganize and add main points

@@

\item Using a probabilistic logical inference approach to the learning task, which builds a more informative structure than state of the art machine learning algorithms

\item A basic application of graph analysis on the learned model to improve results in a way not available to traditional machine learning approaches

\item An open-source implementation, \app, of this approach applied to a set of 256 real world benchmarks. \app identify XX new misconfigurations errors on YY of these files.
\end{enumerate}

>>>>

% Encore also used association rule learning, but did not describe why it is useful for verification in particular,
%   or how it contrasts with other ML techniques that are less appropriate for verification (NN).
\item Describing the logical foundation of using association rule learning to build a probabilistic specification for configuration files. 
      We contrast this with the application of other machine learning techniques, such as neural networks, in verification.

% We can analyze the rules we have learned as a graph to sort the errors, not just by weight, but also importance
% need one more thing we can do with this graph
% This is only possible when we have learned association rules, not possible with NN
\item Analyzing the learned model to further refine the generated specification. 
      We highlight why these analysis techniques are uniquely possible in an association rule learning approach.

% The problem is intractable for off-the-shelf data mining solutions (see Encore).
% In addition to the optimizations Encore used, we add new ones that make our tool even better.  
\item An open-source implementation, \app, of this approach, which uses various domain specific optimizations to make the solution efficient. 
      We also evaluate \app on a set of 256 real world benchmarks, and identify XX new misconfigurations errors on YY of these files.
\end{enumerate}

@@
